Clustering time series based on probability distributions across temporal granularities

### 2021-11-16 main.Rmd
caption of table 2

```{r range-parameter, fig.cap="Range of parameters for different scenarios"}
knitr::include_graphics("figs/simulation_table.png")
```

>>>>

```{r range-parameter, fig.cap="The range of parameters used for the validation study, for the three different scenarios, number of simulations for each design, differences between means across granularities and series lengths. "}
knitr::include_graphics("figs/simulation_table.png")
```
